Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-07-04 doc/PRF2022/PRF_main.tex

\begin{figure}[h!]
\begin{center}
  \hspace{-1cm}
  \includegraphics[height=0.27\textheight]{Nb198a_inset.pdf}
  \hspace{-0.85cm}
  \includegraphics[height=0.27\textheight]{Nb198b_eta_inset.pdf}\\
  \includegraphics[height=0.27\textheight]{Nb198c_eta_inset.pdf}
  \includegraphics[height=0.27\textheight]{Nb198d_eta_inset.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows $N_b = 198$ particles confined to a square with random 
  positions and orientation.
  Depending on the boundary condition \eqref{eq:bc-type},
  the particles self-assemble into distinct configurations.
  Panel (b) is for $b=1$ and the boundary condition mimicks that
  of an amphiphilic particle. 
  Panel (c) is for $b=2$ which gives rise to a multilamellar configuration. 
  In panel (d), the case $b = 0$ is for a water structure with
  positive/negative charge. 
  The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.
    All figure insets are configurations using $N_b=60$ sharing with the same color map.}
\end{caption}
\end{figure}

@@

\begin{figure}
  \begin{center}
%  \includegraphics[width=0.49\textwidth]{Relax_Energy_inset.pdf}
%\includegraphics[width=0.49\textwidth]{relax_E.pdf}
%\includegraphics[width=0.49\textwidth]{relax_LOP.pdf} 
\includegraphics[width=1.0\textwidth]{relax_E_LOP.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
  A:  The free energy \eqref{eq:free_energy} is decreasing
    in the mobility problem formulation.  The initial energies
    are for the configuration in Figure \ref{fig:relax}a
    and the final energies are for the near-equilibrium
    configurations Figure \ref{fig:relax}b--c, respectively. 
    The red curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles. B: The local order parameter $\tilde{S}_2$ for all 6 relaxation runs. The near-equilibrium configurations depend on the initial configuration and the results show that 
    the striated configurations have largest value of order parameter for both $N_b=60$ and $N_b=198$ cases.
  }
\end{figure}

>>>>

\begin{figure}[h!]
\begin{center}
  \hspace{-1cm}
  \includegraphics[height=0.3\textheight]{Nb198a_inset.pdf}
  \hspace{-0.85cm}
  \includegraphics[height=0.3\textheight]{Nb198b_eta_inset.pdf}\\
  \includegraphics[height=0.3\textheight]{Nb198c_eta_inset.pdf}
  \includegraphics[height=0.3\textheight]{Nb198d_eta_inset.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows $N_b = 198$ particles confined to a square with random 
  positions and orientation and the inset shows $N_b=60$ particles configuration.
  Depending on the boundary condition \eqref{eq:bc-type},
  the particles self-assemble into distinct configurations.
  Panel (b) is for $b=1$ and the boundary condition mimicks that
  of an amphiphilic particle. 
  Panel (c) is for $b=2$ which gives rise to a multilamellar configuration. 
  In panel (d), the case $b = 0$ is for a water structure with
  positive/negative charge. 
  The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.
 Panel (b)--(d) insets are configurations using $N_b=60$ sharing with the same color map.}
\end{caption}
\end{figure}

@@

\begin{figure}
  \begin{center}
%  \includegraphics[width=0.49\textwidth]{Relax_Energy_inset.pdf}
%\includegraphics[width=0.49\textwidth]{relax_E.pdf}
%\includegraphics[width=0.49\textwidth]{relax_LOP.pdf} 
\includegraphics[width=1.0\textwidth]{relax_E_LOP.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
  A:  The free energy \eqref{eq:free_energy} decreases
    in the mobility problem formulation.  The initial energies
    are for the configuration in Figure \ref{fig:relax}a
    and the final energies are for the near-equilibrium
    configurations as shown in Figure \ref{fig:relax}b--d, respectively.
    The black curves are the energies for the $N_b=60$ cases and  
    the red curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles. B: The local order parameter $\tilde{S}_2$ for all 6 relaxation runs. 
    The curve styles are identical to the ones in panel A.
    The near-equilibrium configurations depend on the initial configuration and the results show that for both $N_b=60$ and $N_b=198$ cases, bilayer and multi-lamellar configurations have similar trend in self-assembly in term of the local order parameter. The results of the striated configuration depend on the initial setup.
  }
\end{figure}
